The low-frequency Murchison radio environment:\\interference analysis and mitigation

### 2014-09-11 articles/2014/MWA-Radio-Environment/mwa-radio-environment.tex
Adding seperated plots

\noindent\begin{figure*}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=18cm]{img/plot-rfi-per-set}\vspace{-1cm}
\caption{..}
\label{fig:rfi-per-set}
\end{center}
\end{figure*}

\noindent\begin{figure*}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=18cm]{img/2014-03-17-dvb-stddevs}\vspace{-1cm}
\caption{..}
\label{fig:rfi-per-set}
\end{center}
\end{figure*}

>>>>

\noindent\begin{figure*}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=18cm]{img/plot-rfi-per-set-eor}\vspace{-1cm}
\caption{..}
\label{fig:rfi-per-set-eor}
\end{center}
\end{figure*}

\noindent\begin{figure*}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=18cm]{img/plot-rfi-per-set-gleam}\vspace{-1cm}
\caption{..}
\label{fig:rfi-per-set-gleam}
\end{center}
\end{figure*}

\noindent\begin{figure*}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=18cm]{img/2014-03-17-dvb-stddevs}\vspace{-1cm}
\caption{..}
\label{fig:dvb-stddevs}
\end{center}
\end{figure*}

\noindent\begin{figure}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=9.1cm]{img/lognlogs-residual}
\caption{Log N log S for residuals}
\label{fig:lognlogs-residuals}
\end{center}
\end{figure}

\noindent\begin{figure}
\begin{center}\hspace*{-0.2cm}\includegraphics[width=9.1cm]{img/lognlogs-rfi}
\caption{Log N log S for RFI }
\label{fig:lognlogs-rfi}
\end{center}
\end{figure}
